Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2016-01-31 document/ms.tex
adding fits
A few words for the abstract

Hi.

@@

The transit method of exoplanet detection and characterization has been
demonstrated as a powerful method for building systematic catalogs of
exoplanets.
Despite the great success of the \kepler\ Mission with thousands of planet
discoveries \citep{Burke:2014, Rowe:2015}, current methods for exoplanet
discoveries are currently limited in the range of orbital periods that can be
studied.
Specifically, the standard transit search procedures only discover signals
with at least three observed transits \citep[for example][]{Petigura:2013,
Burke:2014, Rowe:2015}.
For \kepler, with a baseline of about four years, this sets an upper limit on
the detectable periods of just over a year.
In the Solar System, Jupiter---with a period of 12 years---dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, it would be missed by most existing transit search procedures.
It is possible to discover long-period planets like this using targeted radial
velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014} but the
cost of implementing a systematic RV search is substantially higher than
searching the existing and forthcoming photometric data for single transits.

@@

A qualitatively different approach to planet search is employed by the
\project{Planet Hunters} (PH)
project\footnote{\url{http://www.planethunters.org/}} \citep{Fischer:2012}.
PH is a ``citizen science'' project where visitors to the website look at
sections of light curve and mark the locations of transits that can be
identified visually.
Visual inspection can be a useful search technique for large single transits
because humans are able to robustly distinguish transit signals from the noise
and this project has yielded some promising long-period candidates and
confirmed planets \citep[for example][]{Wang:2013}.
One shortcoming of the PH method is that it can be difficult to fully quantify
the performance (completeness and reliability) of the search and PH does not
evaluate their users using synthetic transit signals as is now common practice
in the transit search literature.
This means that the PH sample of candidates cannot be used for robust
population inference.

@@

>>>>

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and extra-Solar planetary systems as a
function of their physical properties.
Transit survey like \kepler\ are most sensitive to planets with shorter
orbital periods than the gas giant planets that dominate the dynamics of our
Solar System.
We performed a fully-automated search for the transits of long-period
exoplanets in the archival \kepler\ light curves and announce XXX planet
candidates.
Since our method involves no human intervention, we empirically characterize
the completeness and reliability of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter and with orbital periods longer than 700 days to be $\dd
N = YYY \pm ZZZ\dd \ln P \dd \ln R$.

@@

The transit method of exoplanet detection and characterization has been
demonstrated as a powerful method for building systematic catalogs of
exoplanets.
Despite the great success of the \kepler\ Mission with thousands of planet
discoveries \citep{Burke:2014, Rowe:2015}, current methods for exoplanet
discoveries are currently limited in the range of orbital periods that can be
studied.
Specifically, the standard transit search procedures only discover signals
with at least three observed transits \citep[for example][]{Petigura:2013,
Burke:2014, Rowe:2015}.
For \kepler, with a baseline of about four years, this sets an absolute upper
limit on the detectable periods of about two years.
In the Solar System, Jupiter---with a period of 12 years---dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, it would be missed by most existing transit search procedures.
It is possible to discover long-period planets like this using targeted radial
velocity (RV) surveys \citep[for example][]{Butler:2006, Knutson:2014}
\dfmtodo{CITE Bryan \etal} but the cost of implementing a systematic RV search
is substantially higher than searching the existing and forthcoming
photometric data for single transits.

@@

A qualitatively different approach to planet search is employed by the
\project{Planet Hunters} (PH)
project\footnote{\url{http://www.planethunters.org/}} \citep{Fischer:2012}.
PH is a ``citizen science'' project where visitors to the website look at
sections of light curve and mark the locations of transits that can be
identified visually.
Visual inspection can be a useful search technique for large single transits
because humans are able to robustly distinguish transit signals from the noise
and this project has yielded some promising long-period candidates and
confirmed planets \citep[for example][]{Wang:2013} \dfmtodo{CITE Wang 2015}.
One shortcoming of the PH method is that it can be difficult to fully quantify
the performance (completeness and reliability) of the search and PH does not
evaluate their users using synthetic transit signals as is now common practice
in the transit search literature \dfmtodo{is this still true?}.
This means that the PH sample of candidates cannot be used for robust
population inference.

To study the occurrence rate of long-period exoplanets, we developed a
fully-automated method for searching the archival \kepler\ light curves for
these systems with only one or two transits.

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/full_sample.pdf}
\end{center}
\caption{%
Blah.
\figlabel{full-sample}}
\end{figure}
